\null
\vfill
\begin{center}
\end{center}
\vfill

\prefacesection{Acknowledgments}

This project has taken me on an incredible journey filled with equal amounts joy/excitement and self-doubt. Throughout all the ups and downs, hard days and long nights, has been my wife, Kendal. She's been incredibly level-headed and strong during the past 6 years, which was a major reason I was able to do what I did here. I'd also like to thank my son Jensen for making me laugh and smile more than I ever have in my life over the past year. I hope he never stops enjoying life as much as he does now. Lastly, I want to thank my mother who moved her entire life over 600 miles last year to help us take care of Jensen so I could finish this work. Without all three of you, I would not be who I am today.

This project would not have been possible without the incredibly smart and dedicated folks in the BONuS12 group. Gail Dodge, my dissertation director, has been an unwavering source of support and knowledge throughout my time at ODU. I always enjoy working alongside people with such drive and intellect. It forces me to do more and work harder. Sebastian Kuhn, Stephen Bueltmann, Mohammad Hattawy, Gabriel Charles, David Payette, and Jiwan Poudel have served as those motivating people throughout. I want to thank them and the rest of the BONuS12 team for all the help and guidance in this work.

Lastly, I want to thank everyone I have had the pleasure of working with at JLab. I need to thank Maurizio Ungaro and Harut Avakian, particularly, for answering my seemingly endless questions about GEMC and RGA analysis, respectively. Thank you to Eric Christy, another member of the BONuS12 group, who helped me with his model to extract the differential cross sections. Finally, I want to thank the members of my dissertation committee, who all have provided feedback and remained flexible through the strange/difficult times we are currently going through. \\ \\
\noindent
Thank you all so much. It has been a pleasure.


